---
title: "figures"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options( "ReporteRs-fontsize" = 12)
```

[Correlation Analyses in R](http://www.sthda.com/english/wiki/print.php?id=112)

_Correlation matrix analysis is very useful to study dependences or associations between variables_

##load data
```{r}
figure_list <- list()
dir.create("figures")
```
## import library
```{r include=FALSE}
library(tidyverse)
library(flextable)
library(ggpubr)
library('ReporteRs')
library(survival)
library(Cairo)
library(officer)
```

## content
### 01 correlation test 
```{r}
data("mtcars")
my_data <- mtcars[, c(1,3,4,5,6,7)]
res <- cor.test(my_data$wt, my_data$mpg, 
                    method = "pearson")
res
```

### 02 correlation matrix
#### flattenCorrMatrix
```{r}
library("Hmisc")
res2 <- rcorr(as.matrix(my_data))
flattenCorrMatrix(res2$r, res2$P)
```
####corstars
```{r}
mcor<-round(cor(mtcars),2)
corstars(mtcars[,1:7])
```

### 03 correlation visualizaton
####corrplot() function to plot a correlogram
```{r}
res <- cor(my_data)
library(corrplot)
# Insignificant correlations are leaved blank
corrplot(res2$r, type="upper", order="hclust", 
         p.mat = res2$P, sig.level = 0.01, insig = "blank")

```

####scatter plots
```{r}
library("PerformanceAnalytics")
my_data <- mtcars[, c(1,3,4,5,6,7)]
chart.Correlation(my_data, histogram=TRUE, pch=19)
```

####heatmap
```{r}
# Get some colors
col<- colorRampPalette(c("blue", "white", "red"))(20)
heatmap(x = res, col = col, symm = TRUE)
```

### 04 correlation scatter plot
```{r}
library("ggpubr")
ggscatter(my_data, x = "mpg", y = "wt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Miles/(US) gallon", ylab = "Weight (1000 lbs)")
```
### 05 An R function to do all you need
**rquery.cormat()**: 
    for calculating and visualizing easily acorrelation matrix
```{r}
source("http://www.sthda.com/upload/rquery_cormat.r")
col<- colorRampPalette(c("blue", "white", "red"))(20)
rquery.cormat(my_data, type = "lower", col = col)
#Draw a heatmap
cormat<-rquery.cormat(my_data, graphType="heatmap")
#Format the correlation table
rquery.cormat(my_data, type="flatten", graph=FALSE)
```

## export to ppt
###single pptx file👍
```{r}
library('ReporteRs')
#new pptx
pptx.file = "figures/editable-survival-curves.pptx"
doc <- pptx()
for (it in figure_list) {
  doc <-doc %>%
  addSlide(slide.layout = "Two Content") %>% # Add a new slide into the ppt document
  addTitle("Survival Curves: Editable Vector Graphics") %>% # Add a slide title
  addPlot(function()
  print(it, newpage = FALSE), # Print the survival curves in the powerpoint
  vector.graphic = TRUE) # Make it editable
} -> report
writeDoc(report, file = pptx.file )# write the document to a file
```

###multiple pptx file 👍
```{r}
pptx.file = str_c("figures/",names(figure_list),".pptx")

black_pptx <- function(p, filename){
  pptx() %>%
  addSlide(slide.layout = "Two Content") %>% # Add a new slide into the ppt document
  addTitle("Survival Curves: Editable Vector Graphics") %>% # Add a slide title
  addPlot(function()
  print(p, newpage = FALSE), # Print the survival curves in the powerpoint
  vector.graphic = TRUE)  %>% # Make it editable
  writeDoc(file = filename)
}
map2(figure_list, pptx.file, black_pptx)
```
