---
title: "figures"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options( "ReporteRs-fontsize" = 12)
```

##load data
```{r}
set.seed(1234)
wdata = data.frame(
   sex = factor(rep(c("F", "M"), each=200)),
   weight = c(rnorm(200, 55), rnorm(200, 58)))
head(wdata, 4)
figure_list <- list()
dir.create("figures")
```
## import library
```{r include=FALSE}
library(tidyverse)
library(flextable)
library(ggpubr)
library('ReporteRs')
library(survival)
library(Cairo)
library(officer)
```

## Figures list 
### figure 01 Density plot with mean lines and marginal rug
```{r}
ggdensity(wdata, x = "weight",
   add = "mean", rug = TRUE,
   color = "sex", fill = "sex",
   palette = c("#00AFBB", "#E7B800"))
```

###figure 02 Histogram plot with mean lines and marginal rug
```{r}
gghistogram(wdata, x = "weight",
   add = "mean", rug = TRUE,
   color = "sex", fill = "sex",
   palette = c("#00AFBB", "#E7B800"))
```

### figure 03 Box plots with jittered points
```{r}
# Load data
data("ToothGrowth")
df <- ToothGrowth
head(df, 4)
p <- ggboxplot(df, x = "dose", y = "len",
                color = "dose", palette =c("#00AFBB", "#E7B800", "#FC4E07"),
                add = "jitter", shape = "dose")
# Add p-values comparing groups
 # Specify the comparisons you want
my_comparisons <- list( c("0.5", "1"), c("1", "2"), c("0.5", "2") )
p + stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 50)
```

### figure 04 Violin plots with box plots inside
```{r}
data("ToothGrowth")
df <- ToothGrowth
# Change fill color by groups: dose
# add boxplot with white fill color
ggviolin(df, x = "dose", y = "len", fill = "dose",
         palette = c("#00AFBB", "#E7B800", "#FC4E07"),
         add = "boxplot", add.params = list(fill = "white"))+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif")+ # Add significance levels
  stat_compare_means(label.y = 50)                                      # Add global the p-value
```

###figure 05 Ordered Bar plots
```{r}
# Load data
data("mtcars")
dfm <- mtcars
# Convert the cyl variable to a factor
dfm$cyl <- as.factor(dfm$cyl)
# Add the name colums
dfm$name <- rownames(dfm)
ggbarplot(dfm, x = "name", y = "mpg",
          fill = "cyl",               # change fill color by cyl
          color = "white",            # Set bar border colors to white
          palette = "jco",            # jco journal color palett. see ?ggpar
          sort.val = "desc",          # Sort the value in dscending order
          sort.by.groups = FALSE,     # Don't sort inside each group
          x.text.angle = 90           # Rotate vertically x axis texts
          )
```

###figure 06 Dot charts
```{r}
ggdotchart(dfm, x = "name", y = "mpg",
           color = "cyl",                                # Color by groups
           palette = c("#00AFBB", "#E7B800", "#FC4E07"), # Custom color palette
           sorting = "ascending",                        # Sort value in descending order
           add = "segments",                             # Add segments from y = 0 to dots
           ggtheme = theme_pubr()                        # ggplot2 theme
           )
```

```{r}
ggdotchart(dfm, x = "name", y = "mpg",
           color = "cyl",                                # Color by groups
           palette = c("#00AFBB", "#E7B800", "#FC4E07"), # Custom color palette
           sorting = "descending",                       # Sort value in descending order
           add = "segments",                             # Add segments from y = 0 to dots
           rotate = TRUE,                                # Rotate vertically
           group = "cyl",                                # Order by groups
           dot.size = 6,                                 # Large dot size
           label = round(dfm$mpg),                        # Add mpg values as dot labels
           font.label = list(color = "white", size = 9, 
                             vjust = 0.5),               # Adjust label parameters
           ggtheme = theme_pubr()                        # ggplot2 theme
           )
```

### figure 07 survival analysis
```{r}
# Fit survival curves
fit<- survfit(Surv(time, status) ~ sex, data = lung)
# Visualize
library("survminer")
p <- ggsurvplot(fit, data = lung,
         surv.median.line = "hv", # Add medians survival
         pval = TRUE,             # Add p-value and tervals
        
         conf.int = TRUE,        # Add the 95% confidence band
         risk.table = TRUE,      # Add risk table
         tables.height = 0.2,
         tables.theme = theme_cleantable(),
         palette = "jco",
         ggtheme = theme_bw()
    )
print(p)
```

##Export to eps or pdf
###- 
```{r}
ggsave(filename = "figures/survival-curves-01.eps",
       plot = print(p),
       device = cairo_ps)
```
###-
```{r}
cairo_ps(filename = "figures/survival-curves-02.eps",
         width = 7, height = 7, pointsize = 12,
         fallback_resolution = 300)
print(p)
dev.off()
```


##figures list and ppt file 
 - is flextable objector?
 - 
```{r}
figure_list
```


## export to ppt
###single pptx file👍
```{r}
library('ReporteRs')
#new pptx
pptx.file = "figures/editable-survival-curves.pptx"
doc <- pptx()
for (it in figure_list) {
  doc <-doc %>%
  addSlide(slide.layout = "Two Content") %>% # Add a new slide into the ppt document
  addTitle("Survival Curves: Editable Vector Graphics") %>% # Add a slide title
  addPlot(function()
  print(it, newpage = FALSE), # Print the survival curves in the powerpoint
  vector.graphic = TRUE) # Make it editable
} -> report
writeDoc(report, file = pptx.file )# write the document to a file
```

###multiple pptx file 👍
```{r}
pptx.file = str_c("figures/",names(figure_list),".pptx")

black_pptx <- function(p, filename){
  pptx() %>%
  addSlide(slide.layout = "Two Content") %>% # Add a new slide into the ppt document
  addTitle("Survival Curves: Editable Vector Graphics") %>% # Add a slide title
  addPlot(function()
  print(p, newpage = FALSE), # Print the survival curves in the powerpoint
  vector.graphic = TRUE)  %>% # Make it editable
  writeDoc(file = filename)
}
map2(figure_list, pptx.file, black_pptx)
```
